\documentclass[letterpaper,margin,line,11pt]{resume}
\usepackage[defblank]{paralist}
\usepackage{pdfpages}
\usepackage{anysize}
\usepackage[unicode]{hyperref}
\hypersetup{
    pdftitle={Derek Gonyeo's Resume},
    pdfauthor={Derek Gonyeo},
    pdfborder={0 0 0},
    unicode=true
}
\marginsize{0.5in}{1.8in}{0.5in}{0.5in}
\setdefaultitem{\footnotesize \textbullet}{}{}{}{}{}
\setdefaultleftmargin{0em}{}{}{}{}{}
\setdefaultenum{(a)}{(1)}{}{}{}{}
\newcommand{\rurl}[1]{\hfill {\footnotesize \url{#1}}}
\newcommand{\rdate}[1]{\hfill {\small #1}}
\renewcommand{\employer}[5]{\item[#1] - #2 \rdate{#3} \\* #4 \rurl{#5}}
\begin{document}
\name{\Large Derek W. Gonyeo \hspace{110 mm} \footnotesize derek@gonyeo.com}
\begin{resume}
\section{\mysidestyle Education}
    \begin{compactdesc}
        \item[Rochester Institute of Technology] - Rochester, NY \rdate{September 2012 - December 2016}
        \small
        \\B.S. Computer Science
    \end{compactdesc}

\section{\mysidestyle Experience}
    \begin{asparadesc}
        \employer{Google}{San Francisco, CA} {June 2018 - Present}{\textit{Software Engineer}}{https://fuchsia.dev/}

        \small
        Currently working on the \textit{Component Framework} team, which is
        building out the main model for software execution and isolation on the
        Fuchsia operating system.
        \normalsize

        \employer{CoreOS}{San Francisco, CA} {September 2015 - May 2018}{\textit{Software Engineer}}{https://coreos.com/}

        \small
        Started as an intern, and transferred to a full-time
        position December 2016. Worked on \textit{rkt}, a secure, composable
        container runtime for Linux, \textit{acbuild}, a build system for
        creating images conforming to the App Container spec, and
        \textit{Container Linux}, a Linux distribution designed for frequent and
        reliable security updates.
        \normalsize

        \employer{CloudFlare}{San Francisco, CA} {June 2015 - August 2015}{\textit{Software Engineer Intern}}{https://www.cloudflare.com/}

        \small
        Interned at CloudFlare during the summer of 2015. Helped create
        \textit{gohbase}, an open source HBase client written in Go.
        \normalsize
    \end{asparadesc}

\section{\mysidestyle Languages}
    Rust, Go, C, C++, Haskell
    \hfill 
    \footnotesize 
    (In decreasing order of proficiency)
    \normalsize

\section{\mysidestyle Personal \\ Projects}
    \begin{compactdesc}
        \item[Fuchsia Linux Mode] \rurl{https://goo.gl/qTAWzv} \\
            Wrote design doc detailing user space tools which would allow
            running unmodified Linux executables on the Fuchsia operating
            system.
        \item[Cyanide] \rurl{https://github.com/dgonyeo/cyanide} \\
            Created a console application in Haskell for managing home bar
            inventory and recipes.
    \end{compactdesc}

\section{\mysidestyle Speaking \\ Experience}
    \begin{compactdesc}
        \item[CoreOS Fest 2016] \rurl{https://coreos.com/fest/2016/} \\
            Spoke about the current state of adding support for the rkt
            container runtime to Kubernetes, and future goals for the effort.
        \item[LinuxCon NA 2016] \rurl{http://sched.co/7JVS} \\
            Spoke again about the current state of adding support for the rkt
            container runtime to Kubernetes, but spent more time describing rkt,
            its architecture, and some of its advantages over Docker.
        \item[KubeCon 2016] \rurl{http://sched.co/8K9M} \\
            Spoke about the image specification of the Open Container
            Initiative, and the impact it would have on the container ecosystem
            once it reached a stable release.
        \item[CoreOS Fest 2017] \rurl{https://coreos.com/fest/} \\
            Spoke about a new tool called the Container Linux Config Transpiler,
            covering what it was, how it fit into the Container Linux tooling,
            and benefits users could expect to gain by using it.
    \end{compactdesc}

\section{\mysidestyle Extracurricular \\ Activities}
    \begin{compactdesc}
        \item[Computer Science House] \hfill Septemer 2012 - Dec 2016 \\
            Member, Financial Director, System Administrator
    \end{compactdesc}

\end{resume}
\end{document}
